---
title: "p8105_hw1_pm2995"
author: "Priyal"
date: "9/14/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1


####Creation of a Data Frame


```{r}
set.seed(1)
df_1 = tibble( 
       random_samp = runif(10,0,5),
       greater_than_2 = random_samp > 2,
       student_name = c("Emma", "Sophia", "Serra", "Elisa", "John", "Jessica","Ross","Kaity", "Jo","Luke"),
       study_year = factor(c("First" , "First", "Second", "First", "Third", "Second", "Second", "Third", "First", "First"))
)

```

####Mean of each variable in Data Frame

* Mean of random sample is `r mean(df_1$random_samp)`

* Mean of the logical vector greater_than_2 is `r mean(df_1$greater_than_2)`

* Mean of character variable is `r mean(df_1$student_name)`

* Mean of factor variable is `r mean(df_1$study_year)`

Mean command did not work for variable student_name and study_year as they both are not numeric and logical variables respectively whose mean can be taken.

####Applying as.numeric function

```{r, results='hide'}
as.numeric(df_1$random_samp)
as.numeric(df_1$greater_than_2)
as.numeric(df_1$student_name)
as.numeric(df_1$study_year)
```

The as.numeric function worked for all the variables except the character variable (student_name). For character variable it gave the warning: NAs introduced by coercion.

